### 2021-05-25 Modules/sec_prlm_FIM.tex
rev03
Final fixes

% This section introduces such a measure for information, and we can also see that this information measure can be used to find bounds on the variance of estimators, and it can be used to approximate the sampling distribution of an estimator obtained from a large sample, and further be used to obtain an approximate confidence interval in case of large sample.

@@

Consider a random variable $x$ for which the pdf is $f\rBrace{x|\theta}$, where $\theta$ is an unknown parameter and $\theta\in\Theta$, with $\Theta$ is the parameter space.

@@

% We define $l\rBrace{x|\theta} = \log{f\rBrace{x|\theta}}$ as the log-likelihood function, and
% \begin{equation*}
%     l^{\prime}\rBrace{x|\theta} = \frac{\partial}{\partial\theta}\log{f\rBrace{x|\theta}}=\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}
% \end{equation*}
% where $f^{\prime}\rBrace{x|\theta}$ is the derivative of $f\rBrace{x|\theta}$ with respect to $\theta$.
% Similarly, we denote the second order derivative of $f\rBrace{x|\theta}$ with respect to $\theta$ as $f^{\prime\prime}\rBrace{x|\theta}$.
% According to the above analysis, if $l^{\prime}\rBrace{X|\theta}$ is close to zero, then it is expected, thus the random variable does not provide much information about $\theta$;
% on the other hand, if $\abs{l^{\prime}\rBrace{X|\theta}}$ or $\abs{l^{\prime}\rBrace{X|\theta}}^{2}$ is large, the random variable provides much information about $\theta$.
% Thus, we can use $\abs{l^{\prime}\rBrace{X|\theta}}^{2}$ to measure the amount of information provided by $X$.
% however, since $X$ is a random variable, we should consider the average case. Thus, we introduce the following definition:
% \begin{definition}
% \emph{Fisher information} (for $\theta$) contained in the random variable $X$ is defined as:
% \begin{equation}
% \label{eq_prlm_FI_def}
%     I\rBrace{\theta}=E_{\theta}\cBrace{\abs{l^{\prime}\rBrace{X|\theta}}^{2}}=\int{}\abs{l^{\prime}\rBrace{X|\theta}}^{2}f\rBrace{x|\theta}dx.
% \end{equation}
% \end{definition}
% We assume that we can exchange the order of differentiation and integration, then
% \begin{equation*}
%     \int{}f^{\prime}\rBrace{x|\theta}dx=\frac{\partial}{\partial\theta}\int{}f\rBrace{x|\theta}dx=0.
% \end{equation*}
% Similarly,
% \begin{equation*}
%     \int{}f^{\prime\prime}\rBrace{x|\theta}dx=\frac{\partial^{2}}{\partial\theta^{2}}\int{}f\rBrace{x|\theta}dx=0.
% \end{equation*}
% It is easy to see that
% \begin{equation*}
%     E_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}=\int{}l^{\prime}\rBrace{x|\theta}f\rBrace{x|\theta}dx=\int{}\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}f\rBrace{x|\theta}dx=\int{}f^{\prime}\rBrace{x|\theta}=0
% \end{equation*}
% Therefore, the definition of Fisher information \eqref{eq_prlm_FI_def} can be rewritten as
% \begin{equation}
% \label{eq_prlm_IeqVar}
%     I\rBrace{\theta}=\text{Var}_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}
% \end{equation}.
% Also, notice that
% \begin{equation*}
%     l^{\prime\prime}\rBrace{x|\theta}=\frac{\partial}{\partial\theta}\vBrace{\frac{f^{\prime}\rBrace{x|\theta}}{f\rBrace{x|\theta}}}=\frac{f^{\prime\prime}\rBrace{x|\theta}f\rBrace{x|\theta}-\abs{f^{\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}=\frac{\abs{f^{\prime\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}-\abs{l^{\prime}\rBrace{x|\theta}}^{2}.
% \end{equation*}
% Therefore,
% \begin{equation*}
%     E_{\theta}\cBrace{l^{\prime\prime}\rBrace{x|\theta}}=\int{\vBrace{\frac{\abs{f^{\prime\prime}\rBrace{x|\theta}}^{2}}{\abs{f\rBrace{x|\theta}}^{2}}-\abs{l^{\prime}\rBrace{x|\theta}}^{2}}f\rBrace{x|\theta}}=\int{f^{\prime\prime}\rBrace{x|\theta}dx}-E_{\theta}\cBrace{l^{\prime}\rBrace{X|\theta}}=-I\rBrace{\theta}.
% \end{equation*}
% Finally, we have another formula to calculate Fisher information:

@@

% To summarize, we have three methods to calculate Fisher information: equations \eqref{eq_prlm_FI_def}, \eqref{eq_prlm_IeqVar} and \eqref{eq_prlm_Ifin}.
% In any problems, using \eqref{eq_prlm_Ifin} is the most convenient choice.

@@

% Suppose that we have a random sample $X_{1},\dots,X_{n}$ coming from a distribution for which the pdf or pmf is $f\rBrace{x|\theta},$ where the value of the parameter $\theta$ is unknown. 
% We will show how to use Fisher information to determine the lower bound for the variance of an estimator of the parameter $\theta$.
% \par
% Let $\hat{\theta}=r\rBrace{X_{1},\dots,X_{n}}=r\rBrace{\vecnot{X}}$ be an arbitrary estimator of $\theta$.
% Assume $E_{\theta}\rBrace{\hat{\theta}}=m\rBrace{\theta}$ and the variance of $\hat{\theta}$ is finite.
% Let us consider the random variable $l^{\prime}\rBrace{\vecnot{X}|\theta}$, it can be shown that $E_{\theta}\cBrace{l^{\prime}\rBrace{\vecnot{X}|\theta}}=0$ and that
% \begin{equation}
% \label{eq_prlm_covThetaLTag}
%     \text{Cov}_{\theta}\cBrace{\hat{\theta},l^{\prime}\rBrace{\vecnot{X}|\theta}}=m^{\prime}\rBrace{\theta}.
% \end{equation}.
% By Cauchy-Schwartz inequality and the definition of $I_{n}\rBrace{\theta},$
% \begin{equation*}
%     \vBrace{\text{Cov}_{\theta}\cBrace{\hat{\theta},l^{\prime}\rBrace{\vecnot{X}|\theta}}}^{2}\leq{}\text{Var}_{\theta}\cBrace{\hat{\theta}}\text{Var}_{\theta}\cBrace{l^{\prime}\rBrace{\vecnot{X}|\theta}}=\text{Var}_{\theta}\cBrace{\hat{\theta}}I_{n}\rBrace{\theta}
% \end{equation*}
% i.e.
In practical applications, where signal is noised and parameters cannot be accurately estimated, having a closed form expression for the FIM naturally leads to seek for a performance bound that will help the user to know when available information is fully utilized.
% \begin{equation*}
%     \vBrace{m^{\prime}\rBrace{\theta}}^{2}\leq{}\text{Var}_{\theta}\cBrace{\hat{\theta}}I_{n}\rBrace{\theta}=nI\rBrace{\theta}=\text{Var}_{\theta}{\cBrace{\hat{\theta}}}
% \end{equation*}
% Finally, we get the lower bound of variance of an arbitrary estimator $\hat{\theta}$ as

@@

% \begin{equation}
% \label{eq_prlm_CramerRao_lim}
%     \text{Var}_{\theta}{\cBrace{\hat{\theta}}}\geq{}\frac{\vBrace{m^{\prime}\rBrace{\theta}}^{2}}{nI\rBrace{\theta}}
% \end{equation}
% where 
% The inequality \eqref{eq_prlm_CramerRao_lim} is called the \emph{information inequality}, and also known as the \emph{Cram\'er-Rao inequality} in honor of the Sweden statistician H. Cram\'er Indian statistician C. R. Rao who independently developed this inequality during the 1940s. 
% The information inequality shows that as $I_{\theta}$ increases, the variance of the estimator decreases, therefore, the quality of the estimator increases, that is why the quantity is called “information”.
% \par
% If $\hat{\theta}$ is an unbiased estimator, then $m\rBrace{\theta}=E_{\theta}\rBrace{\hat{\theta}}=\theta$, $m^{\prime}\rBrace{\theta}=1$.
% Hence, by the information inequality, for unbiased estimator $\hat{\theta}$,

@@

    \text{Var}_{\theta}\cBrace{\hat{\theta}}\geq\frac{1}{nI\rBrace{\theta}}.

@@

The right hand side is always called the Cram\'er-Rao lower bound (CRLB): under certain conditions, no other unbiased estimator of the parameter $\theta$ based on an i.i.d sample of size $n$ can have a variance smaller than CRLB.

@@

Suppose now there are more than one parameters in the distribution model, that is, the random variable $X\sim{}f\rBrace{x|\vecnot{\theta}}$ with $\vecnot{\theta}=\rBrace{\theta_{0},\dot,\theta_{k-1}}^{T}$.

@@

From \eqref{eq_prlm_multiVar_CRLB}, it is obvious that when $I$'th determinant is increased, the CRLB decreases which implicates that the measuring is more informative and though not necessarily obtainable, an optimal estimator will achieve higher accuracy in such scenario.

>>>>

@@

Consider a random variable $x$ for which the PDF is $f\rBrace{x|\theta}$, where $\theta$ is an unknown parameter and $\theta\in\Theta$, with $\Theta$ is the parameter space.

@@

@@

@@

In practical applications, where signal is noisy and parameters cannot be accurately estimated, having a closed form expression for the FIM naturally leads to seek for a performance bound that will help the user to know when available information is fully utilized.

@@

@@

    \text{Var}_{\theta}\cBrace{\hat{\theta}}\geq{}I^{-1}\rBrace{\theta}.%\frac{1}{nI\rBrace{\theta}}.

@@

The right hand side is the CRLB: under certain conditions, no other unbiased estimator of the parameter $\theta$ can have a variance smaller than CRLB.

@@

Suppose now there are more than one parameter in the distribution model, that is, the random variable $X\sim{}f\rBrace{x|\vecnot{\theta}}$ with $\vecnot{\theta}=\rBrace{\theta_{0},\dot,\theta_{k-1}}^{T}$.

@@

From \eqref{eq_prlm_multiVar_CRLB}, it is obvious that when $I$'th determinant is increased, the CRLB decreases which implicates that the data is more informative and though not necessarily obtainable, an optimal estimator will achieve higher accuracy in such scenario.

### 2021-05-25 Modules/sec_prlm_FIR_IIR.tex
Final fixes

    The FIR filter is a merely a delay-and-sum mechanism, therefore its memory is finite and equal to the number of taps in the final filter's configuration as in Fig.~\ref{fig_FIR_arch}.

@@

We consider the same ULA as in Sec.~\ref{sec:prlm_propWaveField}, where a target of interest is placed at $\vpt$.
Focusing on a far field localization problem, DOA and target range are to be estimated. 
For simplicity, we assume an anechoic environment, an array of identical omni-directional sensors and a stationary target of interest.

@@

\par As in RADAR applications, the target is assumed to emit a signal $s\rBrace{t}$, where for convenience $s\rBrace{t=0}$ is the signal which impinges $\vpi{0}$ .

@@

\vecnot{\F{x}}\rBrace{\omega,\theta_{d}}=\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}

@@

where $S\rBrace{\omega}$ is the Fourier transform of $s\rBrace{t}$ and $\vdO$ denotes the steering vector whose $n$'th element is

@@

    d_{n}\rBrace{\omega,\theta_{d}} = \exp{\rBrace{-j\omega\tau_{n}\rBrace{\theta}}}.

@@

    Z\rBrace{\omega,\theta_{d}} = \vecnot{\beta}^{T}\rBrace{\omega}\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}.

@@

Z\rBrace{\omega,\theta} = \F{s}\rBrace{\omega}\sum_{n=0}^{N-1}\beta_{n}\rBrace{\omega}\exp\Brack{-jn\theta},

@@

Also notable is the stability issues of the IIR filter.

@@

Motivated by the IIR efficiency, we wish to find the spatial structure that will be analogous to the IIR filer design.

>>>>

    The FIR filter is a merely a delay-and-sum mechanism, therefore its memory is finite and equals to the number of taps in the final filter's configuration as in Fig.~\ref{fig_FIR_arch}.

@@

% We consider the same ULA as in Sec.~\ref{sec:prlm_propWaveField}, where a target of interest is placed at $\vpt$.
% Focusing on a far field localization problem, DOA and target range are to be estimated. 
% For simplicity, we assume an anechoic environment, an array of identical omni-directional sensors and a stationary target of interest.

@@

% \par As in RADAR applications, the target is assumed to emit a signal $s\rBrace{t}$, where for convenience $s\rBrace{t=0}$ is the signal which impinges $\vpi{0}$ .

@@

\vecnot{\F{x}}\rBrace{\omega,\theta_{d}}=\vecnot{d}\rBrace{\omega,\theta_{d}}\F{s}\rBrace{\omega}

@@

where $S\rBrace{\omega}$ is the Fourier transform of $s\rBrace{t}$ and $\vecnot{d}_{\theta_{d}}$ denotes the steering vector whose $n$'th element is

@@

    d_{n}\rBrace{\omega,\theta_{d}} = \exp{\rBrace{-j\omega\tau_{n}\rBrace{\theta_{d}}}}.

@@

    Z\rBrace{\omega,\theta_{d}} = \vecnot{\beta}^{T}\rBrace{\omega}\vecnot{d}_{\theta_{d}}\rBrace{\omega}\F{s}\rBrace{\omega}.

@@

Z\rBrace{\omega,\theta} = \F{s}\rBrace{\omega}\sum_{n=0}^{N-1}\beta_{n}\rBrace{\omega}\exp\Brack{-jn\theta\rBrace{\omega}},

@@

Also notable is the inherent stability of the FIR filter.

@@

Nevertheless, motivated by the IIR efficiency, we wish to find the spatial structure that will be analogous to the IIR filter design.

### 2021-05-25 Modules/sec_prlm_array_perf.tex
Final fixes

The reader may notice that $\psi$ is exactly the electric phase $\theta$ defined in \eqref{eq:thetaULA} therefore, throughout the rest of the work, we use the $\theta$ notation. 
Also, we choose to plot beampatterns using $\Delta\theta = \theta\rBrace{\theta_{d}} - \theta\rBrace{\theta_{s}}$, where $\theta_{s}$ is the steering angle of the array, it centers the mainlobe, enabling convenient comparison.

@@

and for uniformly weighted ULAs with no feedback, it is known \cite{van2004optimum} that $\mathcal{D} = N$.

>>>>

% The reader may notice that $\psi$ is exactly the electric phase $\theta$ defined in \eqref{eq:thetaULA} therefore, throughout the rest of the work, we use the $\theta$ notation. 
% Also, we choose to plot beampatterns using $\Delta\theta = \theta\rBrace{\theta_{d}} - \theta\rBrace{\theta_{s}}$, where $\theta_{s}$ is the steering angle of the array, it centers the mainlobe, enabling convenient comparison.

@@

and for uniformly weighted ULAs, it is known \cite{van2004optimum} that $\mathcal{D} = N$.

### 2021-05-25 Modules/sec_prlm_localization.tex
Final fixes

In the wide and very active research field of parametric estimation, one issue of relevance to this thesis is the sensor-array based localization - i.e. positional parameters estimation of impinging signal which is measured by an array of sensors.

@@

Following the classical methods overview in \cite{krim1996two}, localization estimators may be divided to two main groups - i.e. \textit{spectral-based} and \textit{parametric}.

@@

The later approach, of parameter estimation assumes a physical model of the experimental scenario.
Then, spatio-temporal estimators take advantage of not only the spatial diversity but also from the temporal information in order to increase the overall SNR.

@@

In the following, a basic overview of some classical algorithms are presented.

>>>>

In the wide and very active research field of parametric estimation, one issue of relevance to this thesis is localization.

@@

Following the classical methods overview in \cite{krim1996two}, localization estimators may be divided to two main groups - \textit{spectral-based} and \textit{parametric}.

@@

The later approach, of parameter estimation, assumes a physical model of the experimental scenario.
% Then, spatio-temporal estimators take advantage of not only the spatial diversity but also from the temporal information in order to increase the overall SNR.

@@

In the following, a basic overview of some classical algorithms is presented.

### 2021-05-25 Modules/sec_prlm_propWaveField.tex
Final fixes

\par For example, in the context of ULA, assuming far field scenario, the impinging waves are treated as constant phase planes as in \eqref{eq_prlm_waveEq_finSol}.

>>>>

\par For example, in the context of ULA, assuming a far field scenario, the impinging waves are treated as constant phase planes as in \eqref{eq_prlm_waveEq_finSol}.

### 2021-05-25 Modules/sec_prlm_timeSpaceSig.tex
Final fixes

As mentioned before, the measurements of the sensor array's elements are fused together, where spatial information resides in the relations between samples taken the same time $t$.
A basic application of the sensor array is the beamformer, designed to enhance signals from certain directions while suppressing other signals from unwanted directions, forming a beam directed to the enhanced direction.  
\begin{figure}[ht!]
    \begin{center}
        \begin{overpic}[width=0.6\linewidth, 
        % grid, 
        tics=10,trim=0 0 0 0]{./Media/arrayProc.png}
        \put(19.5,29.5){\rotatebox{0}{$\theta$}}
        \put(15,21.5){\rotatebox{0}{\tiny{$N-1$}}}
        \put(65,21.5){\rotatebox{0}{\tiny{1}}}
        \put(52,21.5){\rotatebox{0}{\tiny{2}}}
        \put(80,21.5){\rotatebox{0}{\tiny{0}}}
        \put(16,18){\rotatebox{0}{\tiny{$\omega_{N-1}$}}}
        \put(54,18){\rotatebox{0}{\tiny{$\omega_{2}$}}}
        \put(67,18){\rotatebox{0}{\tiny{$\omega_{1}$}}}
        \put(81,18){\rotatebox{0}{\tiny{$\omega_{0}$}}}
        \put(50.5,3.5){\rotatebox{0}{\tiny{$z\rBrace{t}$}}}
        \end{overpic}
    \end{center}
     \caption{ULA based coherent processing of simultaneous spatially sampled signal, measuring a wavefront impinging from DOA $\theta$}
    \label{fig_ULA_imping}
\end{figure}
In complimentary to Fig.~\ref{fig_ULA_sketch}, Fig.~\ref{fig_ULA_imping} adds the processor layer of the beamformer.
\par A temporal snapshot measured by the array at time $t$ is
\begin{equation}
\vecnot{f}\rBrace{t,\vecnot{p}} = \vBrace{f\rBrace{t,p_{0}},\dots,f\rBrace{t,p_{N-1}}}^{T}.
\end{equation}
Considering the CB \cite{van2004optimum}, the output ($z\rBrace{t}$) is expressed by:
\begin{equation}
z\rBrace{t} = \sum_{n=0}^{N-1}{f\rBrace{t,p_{n}}\omega_{n}^{*}},
\end{equation}
where $\omega_{n}$ is a complex weight used for the $n$'th sensor's output, as shown in Fig.~\ref{fig_ULA_imping} and $^{*}$ denotes complex conjugation. 
Consider $s\rBrace{t} = e^{j\omega{t}}$ as a plane wave propagating at temporal frequency $\omega$, and $\theta \in \vBrace{-\frac{\pi}{2},\frac{\pi}{2}}$ as the DOA angle measured with respect to the broadside of the linear array, as shown in Fig.~\ref{fig_ULA_imping}.
The wave signal, spatially sampled by the sensor array inputs is
\begin{equation}
\label{eq_prlm_timeSpace_outputVec}
\vecnot{f}\rBrace{t,\vecnot{p}} = \vBrace{s\rBrace{t},s\rBrace{t-\tau}\dots, s\rBrace{t-\rBrace{N-1}\tau}}^{T},
\end{equation}
where $\tau = \frac{d\cdot{}\cos{\theta}}{c}$ is the propagation delay between consecutive sensors and $c$ is the wave's velocity in the medium.
Considering narrowband signals, the time delay $\tau$ translates to a mere phase shift and the \emph{steering vector} takes the form of
\begin{equation}
\vecnot{d}\rBrace{\theta}=\vBrace{1,e^{-j\omega\tau},\dots,e^{-j\omega\tau\rBrace{N-1}}}^{T}.
\end{equation}
As every impinging signal will cause the excitation of the array elements in the form of a specific steering vector (up to a common additive phase), we define the \emph{array manifold} to be the set of all steering vectors of $\theta\in\left[0,2\pi\right)$, hence it also spans the received signal subspace in the noiseless scenario.

>>>>

As mentioned before, the measurements of the sensor array's elements are utilized together, where spatial information resides in the relations between samples taken the same time $t$.
A basic application of the sensor array is the beamformer, designed to enhance signals from certain directions while suppressing other signals from unwanted directions, forming a beam directed to the enhanced direction.  
\begin{figure}[ht!]
    \begin{center}
        \begin{overpic}[width=0.6\linewidth, 
        % grid, 
        tics=10,trim=0 0 0 0]{./Media/arrayProc.png}
        \put(19.5,29.5){\rotatebox{0}{$\theta$}}
        \put(15,21.5){\rotatebox{0}{\tiny{$N-1$}}}
        \put(65,21.5){\rotatebox{0}{\tiny{1}}}
        \put(52,21.5){\rotatebox{0}{\tiny{2}}}
        \put(80,21.5){\rotatebox{0}{\tiny{0}}}
        \put(16,18){\rotatebox{0}{\tiny{$\omega_{N-1}$}}}
        \put(54,18){\rotatebox{0}{\tiny{$\omega_{2}$}}}
        \put(67,18){\rotatebox{0}{\tiny{$\omega_{1}$}}}
        \put(81,18){\rotatebox{0}{\tiny{$\omega_{0}$}}}
        \put(50.5,3.5){\rotatebox{0}{\tiny{$z\rBrace{t}$}}}
        \end{overpic}
    \end{center}
     \caption{ULA based coherent processing of simultaneous spatially sampled signal, measuring a wavefront impinging from DOA $\theta$}
    \label{fig_ULA_imping}
\end{figure}
In complimentary to Fig.~\ref{fig_ULA_sketch}, Fig.~\ref{fig_ULA_imping} adds the processor layer of the beamformer.
\par A temporal snapshot measured by the array at time $t$ is
\begin{equation}
\vecnot{f}\rBrace{t,\vecnot{p}} = \vBrace{f\rBrace{t,p_{0}},\dots,f\rBrace{t,p_{N-1}}}^{T}.
\end{equation}
Considering the CB \cite{van2004optimum}, the output ($z\rBrace{t}$) is expressed by:
\begin{equation}
z\rBrace{t} = \sum_{n=0}^{N-1}{f\rBrace{t,p_{n}}\omega_{n}^{*}},
\end{equation}
where $\omega_{n}$ is a complex weight used for the $n$'th sensor's output, as shown in Fig.~\ref{fig_ULA_imping} and $^{*}$ denotes complex conjugation. 
Consider $s\rBrace{t} = e^{j\omega{t}}$ as a plane wave propagating at temporal frequency $\omega$, and $\theta \in \vBrace{-\frac{\pi}{2},\frac{\pi}{2}}$ as the DOA angle measured with respect to the broadside of the linear array, as shown in Fig.~\ref{fig_ULA_imping}.
The wave signal, spatially sampled by the sensor array inputs is
\begin{equation}
\label{eq_prlm_timeSpace_outputVec}
\vecnot{f}\rBrace{t,\vecnot{p}} = \vBrace{s\rBrace{t},s\rBrace{t-\tau}\dots, s\rBrace{t-\rBrace{N-1}\tau}}^{T},
\end{equation}
where $\tau = \frac{d\cdot{}\cos{\theta}}{c}$ is the propagation delay between consecutive sensors and $c$ is the wave's velocity in the medium.
Considering narrowband signals, the time delay $\tau$ translates to a mere phase shift and the \emph{steering vector} takes the form of
\begin{equation}
\vecnot{d}\rBrace{\theta}=\vBrace{1,e^{-j\omega\tau},\dots,e^{-j\omega\tau\rBrace{N-1}}}^{T}.
\end{equation}
As every impinging signal will cause the excitation of the array elements in the form of a specific steering vector (up to a common additive phase), we define the \emph{array manifold} to be the set of all steering vectors of $\theta\in\left[0,2\pi\right)$, hence it also spans the received signal subspace in the noiseless scenario.

### 2021-05-25 Modules/sec_stability.tex
Final fixes

As anticipated from \eqref{eq:SF_CB_gainMismatch} and confirmed with the simulations presented in Fig.\ref{fig_stability}, for $r\geq1$ the system is not stable, for the received amplitude may increase (in absolute value) to infinite values.

@@

As a final observation, we address the ``discrete`` behaviour of $z$, i.e. the value (most noticeable in the $r=1.1$ plot) seems to be piecewise constant.

@@

    After simulating the same setup as in Fig.\ref{fig_stability}, we plot the final received amplitude in dB with different choices of $r$.

@@

\par The second question to be asked regards the settling time of the system, for in Fig.~\ref{fig_stability} we easily observe that the settling time of $r=0.6$ (i.e. $\sim{}10$ signal round trips) is substantially shorter than its matching value ($\sim{}50$) when $r=0.9$.
To better understand the phenomenon in Fig.~\ref{fig_stabilityDur}, we plot for each $r$ value, its corresponding settling time.

@@

    Simulation of same setup as in Fig.\ref{fig_stability}.

@@

    The plotted time is also in units of $\tau_{\text{pd}}$ normalized as in Fig.\ref{fig_stability}.

@@

        \hat{\vecnot{d}}^{H}\vecnot{d} =&\ \vecnot{d}^{H}\hat{\vecnot{d}}\\
        =&\ \sum_{n=0}^{N-1}\exp{\rBrace{jn\Delta\theta}} \\

>>>>

As anticipated from \eqref{eq:SF_CB_gainMismatch} and confirmed with the simulations presented in Fig.\ref{fig_stability}, for $r\geq1$ the system is not stable, for the received amplitude may increase (in absolute value) to infinity.

@@

As a final observation, we address the ``discrete`` behaviour of $z$, i.e. the value (most noticeable in the $r=1.1$ plot in Fig.~\ref{fig_stability}) seems to be piecewise constant.

@@

    After simulating the same setup as in Fig.~\ref{fig_stability}, we plot the final received amplitude in dB with different choices of $r$.

@@

\par The second question to be asked regards the settling time of the system.
For example, in Fig.~\ref{fig_stability} we easily observe that the settling time for $r=0.6$ ($\sim{}10$ signal round trips) is substantially shorter than its matching value ($\sim{}50$) when $r=0.9$.
To better understand the phenomenon, we plot for each $r$ value, its corresponding settling time in Fig.~\ref{fig_stabilityDur}.

@@

    Simulation of same setup as in Fig.~\ref{fig_stability}.

@@

    The plotted time is also normalized in units of $\tau_{\text{pd}}$ as in Fig.~\ref{fig_stability}.

@@

        % \hat{\vecnot{d}}^{H}\vecnot{d} =&\ \vecnot{d}^{H}\hat{\vecnot{d}}\\
        \hat{\vecnot{d}}^{H}\vecnot{d} =&\ \sum_{n=0}^{N-1}\exp{\rBrace{jn\Delta\theta}} \\

### 2021-05-25 main/intro.tex
Final fixes

One notable improvement to the convectional beamformer \cite{van2004optimum} was Capon's beamformer  (aka minimum variance distortionless response (MVDR) in acoustics related literature) which attempts to minimize the power contributed by noise and any signals coming from other directions than the DOA of interest, while maintaining a fixed gain

@@

MUSIC (Multiple SIgnal Classification) algorithm \cite{schmidt1986multiple} which decomposes the estimated covariance matrix to its signal and noise eigenvectors, using orthogonal projection exploiting the fact that the noise sub space is orthogonal to the signal subspace.

@@

Adding the fact that sub-optimal methods such as MUSIC were proven to achieve the Cram\'er Rao bound (CRB) under some practical assumptions (e.g. non-coherent signals) \cite{stoica1989music}, these sub optimal estimators are substantially more common in practice. 

@@

First, as in the early stages of the research, the analogy between a spatial (the ULA) and temporal (the FIR) processors, led us to search for the spatial counterpart of another temporal (the IIR) processor, aiming to translate its advantages from the temporal domain to the spatial domain.
Also, classic spatial analysis tools have been gathered to serve as objective tests to the proposed solutions.

@@

Analysis of the spatial structure proves that the desired recursive spatial response is achievable and we show that the advantages of the proposed solution may be expressed with the classic analysis framework.

@@

After close inspection, we conclude in the third part that the carrier frequencies cause this sensitivity and search for ways to mitigate it.

@@

In Chapter~\ref{chap:prelims}, we cover basic concepts of array processing, followed by some emphasize on the localization field of research and finalize with the basic concepts which drive the motivation for this research.

@@

\par In this work, we use the following conventions; vectors and matrices are denoted by lower and upper case bold italic letters respectively. 
$v_{i}$ and $A_{ij}$ are the $i$-th element of the vector $\vecnot{v}$ and the $i,j$-th element of the matrix $\vecnot{A}$.
Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and Hermitian transpose of the matrix $\vecnot{A}$ respectively.

>>>>

One notable improvement to the conventional beamformer \cite{van2004optimum} was Capon's beamformer  (aka minimum variance distortionless response (MVDR)) which attempts to minimize the power contributed by noise and any signals coming from other directions than the DOA of interest, while maintaining a fixed gain

@@

MUSIC (Multiple SIgnal Classification) algorithm \cite{schmidt1986multiple} which decomposes the estimated covariance matrix to its signal and noise eigenvectors, using orthogonal projection exploiting the fact that the noise subspace is orthogonal to the signal subspace.

@@

Adding the fact that sub-optimal methods such as MUSIC were proven to achieve the Cram\'er Rao lower bound (CRLB) under some practical assumptions (e.g. non-coherent signals) \cite{stoica1989music}, these sub optimal estimators are substantially more common in practice. 

@@

First, as in the early stages of the research, the analogy between a spatial (the ULA) and temporal (the FIR) processors, led us to search for the spatial counterpart of another temporal (the IIR) processor, aiming to transfer its advantages from the temporal domain to the spatial domain.
Also, classic spatial analysis tools have been gathered to serve as performance measures to asses to the proposed solutions.

@@

Analysis of the spatial structure proves that the desired recursive spatial response is achievable and we show that the advantages of the proposed solution may be expressed within the classical analysis framework.

@@

After close inspection, we conclude in the third part that the range estimation errors cause this sensitivity and search for ways to mitigate it.

@@

In Chapter~\ref{chap:prelims}, we cover basic concepts of array processing, followed by some emphasize in the field of localization and finalize with the basic concepts which drive the motivation for this research.

@@

% \par In this work, we use the following conventions; vectors and matrices are denoted by lower and upper case bold italic letters respectively. 
% $v_{i}$ and $A_{ij}$ are the $i$-th element of the vector $\vecnot{v}$ and the $i,j$-th element of the matrix $\vecnot{A}$.
% Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and Hermitian transpose of the matrix $\vecnot{A}$ respectively.
